Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-09-01 paper_review/response_20200826.txt

Dear Dr. Endl,

We thank you for organizing the review of our paper, and also
thank the referee for constructive criticism.  We have considered
the referee's remarks carefully and revised our manuscript
accordingly.

Below, we have reproduced the relevant portions of the referee's
report, alongside our responses. A list of changes is appended to
the manuscript using the trackchanges AASTeX macros. A figure
supporting the verification of our SB2 injection-recovery test
has also been uploaded for inspection.

@@

******************************************
REFEREE COMMENT
----------
It appears that TOI 837 b was previously noted as a candidate
planet and IC 2602 member in Nardiello et al. 2020
(https://ui.adsabs.harvard.edu/abs/2020MNRAS.495.4924N/abstract).
If the authors were unaware, it is still worth mentioning this in
the text.

RESPONSE
----------
> Thank you for noting the omission. We have added the relevant
> citation in Section 2.1.

******************************************
REFEREE COMMENT
----------
Sec. 2.1
A number of validation tests are listed, but no detail is
provided about how these tests work. For example, what is the
ghost diagnostic test?

RESPONSE
----------
> For the sake of brevity, we prefer to continue with our
> refererence to Twicken et al., 2018. The optical ghost
> diagnostic test in the SPOC pipeline (Twicken et al., 2018,
> Section 3.7) flags threshold crossing events that are likely to
> be caused by reflections of light from bright sources between
> CCDs. Since few people know what it is, and it will therefore
> confuse rather than clarify, we have omitted it from the
> manuscript.

@@

******************************************
REFEREE COMMENT
----------
Sec. 2.1
Have the authors performed a by-eye search for additional
transits in the light curve?

RESPONSE
----------
> We did perform a by-eye search for additional transits in the
> light curve, and we did not find any compelling events. The
> logical next step -- quantifying our sensitivity through
> injection-recovery simulations -- would be an interesting
> exercise.  For it to be valid, care would need to be taken to
> marginalize out dependence on the detrending method (e.g.,
> David et al 2019 and 2020's experience which led to the
> four-planet V1298 Tau system).  Given the required level of
> effort, we feel this exercise to be outside the scope of the
> present analysis.

@@

******************************************
REFEREE COMMENT
----------
Sec. 2.2
It seems another line of evidence against Star B (rho=5.4 arcsec)
as the host is the difference imaging centroid test mentioned in
Section 2.1, which they state localizes the transit to within 2
arcseconds of the target.

RESPONSE
----------
> Correct -- we have modified the wording in Sec 2.4 to clarify
> this point.

******************************************
REFEREE COMMENT
----------
Given that TOI 837 and Star A have a large contrast but similar
distances, I would expect the two stars to have a large
difference in their expected densities. Can the mean stellar
density from the transit fit be used to further argue that the
planet orbits TOI 837?

RESPONSE
----------
FIXME FIXME FIXME ... maybe it can...

> -Unfortunately, we do not feel that this argument based on the
> stellar density can be convincingly made. The reason is that
> the transit is grazing, and so our "measurement" of the stellar
> density is in fact largely prior-dominated, rather than being
> determined by the transit data. In other words: in fitting the
> transit data, we assume a stellar radius and logg, and we use
> restrictive priors inferred from the star's position on the
> cluster isochrone (see Table 5). If we were to let those priors
> be much less restrictive (say, with logg being uniform from
> 3.8-4.8, or similar), then we would not be able to break the
> classic degeneracy between the impact parameter and Rp/R*. ...
> (....or would this work regardless?)

@@

******************************************
REFEREE COMMENT
----------
Sec. 2.3
Suggest swapping the order of Figures 3 & 4, as the high
resolution imaging is discussed before the ground-based light
curves.

RESPONSE
----------
> Done, thank you for the suggestion.

******************************************
REFEREE COMMENT
----------
Sec. 2.5.1
For the secondary spectral line injection, it is not clear
whether a synthetic spectrum was added to the raw spectrum before
deriving the LSD profile - or whether a synthetic LSD profile was
added to the true profile. It is not clear that the two
procedures would yield the same results.

RESPONSE
----------
> We have updated the manuscript to clarify that the SB2
> grid-search injection and recovery exercise was conducted with
> the secondary signal injected into the LSD profiles, not the
> spectra. 
> 
> To test the validity of this technique, we injected a second
> set of lines to the original spectra, and compared the
> resulting derived LSD profiles. To inject a second set of lines
> to the raw spectrum, we made use of a high SNR CHIRON spectrum
> of a G0 RV standard star, scaled its flux, and blended it with
> the averaged observed spectrum of TOI-837.  We then performed
> the LSD routine on the blended spectrum to derive its LSD
> broadening profile as we would for a normal observation.
> 
> The attached figure shows the resulting LSD profiles from our
> injection test. The left column (black) shows the LSD profiles
> when the secondary signals were injected directly into the LSD
> profile. The right column (red) shows the results of our
> blended spectrum analysis. There is minimal difference between
> the two injection techniques.

@@

RESPONSE
----------
> All phases -- we have revised the text in Sec 3.2 to clarify
> this point.

******************************************
REFEREE COMMENT
----------
Sec. 4.1.2
The statement that TOI 837 lies along the empirical cluster
isochrone and this limits the presence of a companion to be <50%
the brightness seems to be misstated. I believe the authors mean
that TOI 837 appears to lie below the equal-brightness binary
sequence (which sits 0.75 mag above the single star sequence).
This limits a hypothetical companion to be less than the
brightness of the target star (or less than 50% the total system
brightness).

RESPONSE
----------
> Thank you for raising this point. Our original writing was in
> error, because we meant something slightly stronger. If TOI 837
> were an equal-brightness binary system, it would be 0.75
> magnitudes above the single star sequence. However TOI 837 is
> not only not on the equal-brightness binary sequence -- it is
> not at all elevated with respect to the single-star sequence. A
> binary companion with say half the brightness of the primary
> would make the system 0.44 mags brighter than the single star
> sequence. Based on the intrinsic scatter in the HR diagram,
> this is also ruled out.  We (imprecisely) meant this second
> point, and have modified the text accordingly.

******************************************
REFEREE COMMENT
----------
Sec. 4.2.4
It is not immediately clear that the mass-temperature-age
combination of ~1.2 Msun, 5960 K, and 30-45 Myr is incorrect. The
mass-temperature relation for stars in this mass range is not the
same on the pre-main sequence as it is on the main sequence.

RESPONSE
----------
> Looking at the MIST isochrones, it seems that a
> solar-metallicity, 1.1Msun star reaches the ZAMS around
> log(age) of 7.5, or ~32 Myr. So, TOI 837 seems likely to be
> roughly at the ZAMS, rather than particularly early in its
> pre-main sequence contraction.
>
> Regardless, we have modified the wording here to reflect that
> our preference for "Method 2" is linked to our ability to
> more easily quantify its uncertainties (statistical and
> systematic -- see below).

******************************************
REFEREE COMMENT
----------
Sec. 4.2.4
The authors are encouraged to explore the effect of adopting a
different set of evolutionary models. The Dartmouth models of
Feiden (2016), which include a magnetic field prescription, have
been shown to more accurately reproduce the parameters of
pre-main sequence stars. In the mass range of TOI 837 the effects
may not be dramatic, but are likely to be significant compared to
the quoted uncertainty on e.g. the stellar mass. I would expect
that a 10% uncertainty on the stellar mass would be more
realistic (in the sense that it would accommodate systematic
uncertainties) than the currently quoted 1% uncertainty.

@@

******************************************
REFEREE COMMENT
----------
-"The condition for a grazing transit is whether the impact
parameter b is below 1 - Rp/R*" → below should be replaced with
"above" or "greater than".

RESPONSE
----------
> Corrected, thank you.

******************************************
REFEREE COMMENT
----------
Discussion
More emphasis could be placed on the unusually large size of the
planet. Some speculative discussion on the nature of this
inflation could be warranted. Figure 11 might also be revised to
also reflect the effect of insolation (or the data plotted could
be restricted to close-in planets).

RESPONSE
----------
> Thank you for this suggestion. We have added a sub-plot in
> Figure 11 showing planet sizes and orbital periods, with the
> sub-100 Myr old planets emphasized.  We considered also
> including a plot with planet insolations on the ordinate
> instead of orbital periods, but the NASA Exoplanet Archive
> column for planet insolation is much less complete, presumably
> owing to the sparsity of available stellar luminosities.  We
> have also added some words in the discussion to the effect that
> that the young planets could be large because of i) a selection
> effect or ii) atmospheric escape.

@@

******************************************
REFEREE COMMENT
----------
The paper ends on a note about nodal precession. Is it simple to
compute the nodal precession timescale given some reasonable
assumptions? This might help determine how likely it is that the
effect may be observed in the near term.

RESPONSE
----------
> Our thanks for this comment, which prompted us to calculate the
> precession frequency of the orbital axis due to the stellar
> oblateness using equations from Anderson+2018 and Lai+2018. We
> found that given the observed parameters of the system and an
> assumed stellar Love number (k2) equal to that of the Sun, the
> precession period would be 45,000 years. To complete say 1% of
> a precession cycle, which might roughly be what is needed to
> observe noticeable changes, we would need to wait ~450 years.
>
> We have correspondingly modified the last sentence to say
> something more generic, but actually true: more photometry
> should improve our ability to constrain the orbital
> eccentricity, and will let us search for additional transiting
> planets.

### 2020-09-01 paper/ms.tex
update manuscript and response
shifting preference to be TESS+ground, and explaining why.

%\documentclass[12pt,twocolumn,tighten]{aastex63}
\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

\begin{abstract}
  We report the discovery of TOI 837b and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry
  from El Sauce and ASTEP400, and spectroscopy from CHIRON, FEROS, and
  Veloce.  We find that TOI 837 is a $T=9.9$ mag G0/F9 dwarf in the
  southern open cluster IC 2602.  The star and planet are therefore
  $35^{+11}_{-5}$ million years old.  Combining the transit photometry
  with a prior on the stellar parameters derived from the cluster
  color-magnitude diagram, we find that the planet has an orbital
  period of $8.3\,{\rm d}$ and is slightly smaller than Jupiter
  ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$).  From radial
  velocity monitoring, we limit $M_{\rm p}\sin i$ to less than 1.20
  $M_{\rm Jup}$ (3-$\sigma$).  The transits either graze or nearly
  graze the stellar limb.  Grazing transits are a cause for concern,
  as they are often indicative of astrophysical false positive
  scenarios.  Our follow-up data show that such scenarios are
  unlikely.  Our combined multi-color photometry, high-resolution
  imaging, and radial velocities rule out hierarchical eclipsing
  binary scenarios.  Background eclipsing binary scenarios, though
  limited by speckle imaging, remain a 0.2\% possibility.  TOI 837b is
  therefore a validated adolescent exoplanet.  The planetary nature of
  the system can be confirmed or refuted through observations of the
  stellar obliquity and the planetary mass.  Such observations may also
  improve our understanding of how the physical and orbital properties
  of exoplanets change in time.
\end{abstract}

@@

Beyond physical changes, dynamical changes are expected in the
semi-major axes, eccentricities, and stellar obliquities of young
planets.  When the gas disk is present, the planetary semi-major axis
is thought to change in step with the viscous evolution of the disk
\citep{lin_orbital_1996}.  High-eccentricity migration processes
including planet-planet scattering, secular chaos, and Kozai-Lidov
oscillations can also occur \citep[{\it
e.g.},][]{fabrycky_shrinking_2007,chatterjee_dynamical_2008,lithwick_secular_2014}.
The circularization timescale is thought to be such that for any giant
planets that migrated early, their orbits should circularize within
100 million years \citep{zahn_tidal_1977}.

Finding and understanding systems undergoing these evolutionary changes is
a major goal in contemporary exoplanet research.  To identify stars
younger than say 1$\,$\replaced{Gyr}{gigayear}, a number of direct and indirect methods are
available \citep{soderblom_ages_2010}.  The traditional approach is to
isochronally age-date coeval groups of stars, hereafter ``clusters''
\citep[{\it
e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
Young field stars can also be identified isochronally, provided that
they are sufficiently massive \citep{berger_gaia-kepler_2020}.  Other
age indicators include stellar rotation periods, the abundance of
photospheric lithium, and chromospheric diagnostics such as calcium
emission and broadband UV emission.  Studies by, for instance,
\citet{david_discovery_2018} and G{.}~Zhou et al{.}~(2020, submitted)
have combined these methods to age-date individual field stars hosting
transiting planets.  Many of these latter methods were summarized by
\citet{mamajek_improved_2008}, and have since been calibrated by, {\it
e.g.},
\citet{irwin_rotational_2009,barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
and \citet{curtis_tess_2019} for stellar rotation,
\citet{zerjal_chromospherically_2017} for chromospheric activity, and
{\it e.g.}, \citet{berger_identifying_2018} and
\citet{zerjal_galah_2019} for lithium abundances.

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.77\textwidth]{f1b.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf TESS light curve of \tn.}
    {\it Top}:
    \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Starspot-induced variability is the dominant signal; flares are
    shown with red crosses.  Dashed lines indicate the five transits
    observed by TESS over Sectors 10 and 11.  {\it Middle}: Individual
    transits.  Gray lines are the best-fit transit model, which
    includes a local quadratic trend in each window. Gray points are
    2-minute \texttt{PDCSAP} flux measurements, black points are
    binned to 15-minute intervals.  {\it Bottom}: Phase-folded TESS
    transit.  Gray points are 2-minute measurements with the local
    spot-induced variation removed.  Binning at 6-minute intervals
    yields the black points.  The black error-bar shows the median
    uncertainty for the black points.  The gray line shows the
    best-fit model to the TESS data. 
		\label{fig:tessphot}
	}
\end{figure*}

@@

Figure~\ref{fig:tessphot} shows the data.  The dominant modulation
induced by starspots coming into and out of view has a peak-to-peak
amplitude of about 2.3\%, and a period of about 3 days.  The dips are
suggestive of a grazing transiting planet, recurring roughly every 8
days with a depth of about 0.4\%.  A few flares are also visible.  A
phase-folded view of the TESS transits with starspot variability
removed is also shown in Figure~\ref{fig:tessphot}. Our fitting procedure
for the models in these plots is described in
Section~\ref{subsec:planet}.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Scene of \tn.}
    Mean TESS image of \tn\ from Sector~10\added{ on an 11$\times$11
    pixel cutout}, with a logarithmic grayscale\added{ indicating the
    flux in each pixel}. The yellow star is
    the position of \tn.  White circles are resolved Gaia sources with
    $T<16$\replaced{. Brighter stars are larger}{, with brighter stars
    being larger}.  The black \texttt{X} and white \texttt{/} hatches
    show the apertures used to measure the background and target star
    flux, respectively. \replaced{Dashed lines of constant declination
    and right ascension are shown}{The compass shows cardinal
    directions in celestial coordinates. Dashed lines of constant
    declination are separated by 1$'$, while those of right ascension
    are separated by 2$'$}.  Two stars of interest are ``Star A'' and
    ``Star B'', which were excluded as being possible sources of the
    transits.
		\label{fig:scene}
	}
\end{figure}

@@

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.47\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Velocimetry of \tn.} {\it Top:} Radial velocity (RV)
    measurements, with best-fit instrument offsets and jitter terms
    included.  The expected scatter from starspots based on $v\sin i$
    and the photometric modulation amplitude is
    $\sim$300$\,$m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
    orbital ephemeris of \pn.  The planet is not detected.  The dashed black
    line shows a circular Keplerian orbit representing the 3-$\sigma$
    upper mass limit.
    \label{fig:rvs}
	}
\end{figure}

@@

The spectroscopic line profiles were thoroughly examined for any signs
of secondary lines that might indicate the presence of another star,
either associated or in chance alignment with TOI 837. No such set of
lines was found. To set limits on the contributions of a close-by star
to the observed spectrum, we injected a \replaced{second set of lines
to the mean least-squares deconvolution profile}{secondary signal into
the mean least-squares deconvolution profile} derived from the CHIRON
observations.  The injection spanned 10,000 different combinations of
line broadening, velocity separation, and flux ratio $F_2/F_1$.  The
recovery results showed that for rotational broadenings of the
secondary of $5$, $15$, and $25\,\mathrm{km\,s}^{-1}$, we were able to
exclude sources with flux fractions $F_2/F_1$ brighter than roughly
$0.03$, $0.08$, and $0.20$, provided that the secondary was separated
from the primary by at least $\approx 15\,{\rm km\,s}^{-1}$.  At
smaller velocity separations, the injected lines begin to blend with
the target spectrum.
\added{
  We verified these results by injecting secondary lines directly into
  the spectrum and then deriving its LSD broadening profile as we
  would for a normal observation.  The results were nearly identical,
  save for greater computational cost.
}

@@

Assuming an eclipse has been localized to the target star, potential
false positive scenarios include eclipses of a background binary
(BEB), eclipses of a hierarchical system bound to the primary star
(HEB), and the possibility that the eclipses are caused by a
stellar companion, rather than a planetary one (EB).

@@

In ``Method 2'', we \deleted{simply} used the observed location of
\tn\ in the HR diagram and interpolated against the 40$\,$Myr
isochrone.  This method leverages the relative location of \tn\ within
the \deleted{narrow} \cn\ isochrone to derive precise, theoretically
self-consistent constraints on all of the stellar parameters.
Although this approach would fail for a low-mass star, \tn\ is above
the stellar masses where the Gaia photometry and isochrone models
begin to diverge.
\added{
  The statistical uncertainties yielded by this approach are of order
  1\% for the stellar mass and radius.  To quantify the systematic
  uncertainties, we compared the parameters derived from the MIST
  isochrones with those from the
  PARSEC\footnote{\url{http://stev.oapd.inaf.it/cmd}} isochrones
  \citep{bressan_parsec_2012,chen_improving_2014,chen_parsec_2015,marigo_new_2017}.
  The PARSEC isochrones gave a stellar mass 5\% lower, effective
  temperature 3\% lower, logarithmic surface gravity 1\% lower, and
  radius 8\% lower than the MIST isochrones.  For the sake of
  self-consistency, in Table~\ref{tab:starparams} and the ensuing
  analysis we adopted the stellar
  parameters from MIST.  The reported uncertainties are the quadrature
  sum of the statistical and systematic components.
}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f10.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{ 
    {\bf Posterior probabilities of impact parameter, planet-to-star
    size ratio, and stellar density.} Contours are shown at 1, 2, 3,
    and 4-$\sigma$ confidence.  The planet-to-star size ratio
    corresponds to a planet size between $0.68\,R_{\rm Jup}$ and
    $0.97\,R_{\rm Jup}$ (3$^{\rm rd}$--97$^{\rm th}$ percentile).
    This plot was made using \texttt{corner} \citep{corner_2016}.
		\label{fig:subsetcorner}
	}
\end{figure}

We also fitted the available time-series photometry of \pn\ using two
different approaches.  To derive the most precise possible ephemeris,
we fitted the ground and space-based transits simultaneously.  To
derive the physical parameters of the planet, we fitted the TESS data
alone, due to our better understanding of the underlying systematic
trends and the higher precision.

For the TESS \texttt{PDCSAP} light curve, we first eliminated points
that had quality flags corresponding to any of bits $\{3, 4, 6, 8, 11,
12\}$.  This excluded cadences affected by coarse spacecraft pointing,
reaction wheel desaturation events, manual flags, cosmic ray hits, and
straylight from the Earth or Moon being present.  Inspecting the data,
we also manually excluded the two flares shown in
Figure~\ref{fig:tessphot}.  We then trimmed the TESS data to windows
of $\pm 7\,{\rm hr}$ centered on each transit.

Our model for time-series photometry data was an
\citet{exoplanet:agol20} transit with physical and orbital parameters
shared across all transit windows, plus a local quadratic trend
allowed within each window.  Select parameters and priors are listed
in Table~\ref{tab:posterior}, for the TESS-only model.  In brief, we
fitted for the shared stellar parameters $\{\log g, R_\star, u_0,
u_1\}$, and the shared planetary parameters $\{t_0, P, b, \log(R_{\rm
p}/R_\star)\}$.  There were also three free trend parameters for each
transit window to account for the local rotational variability.  In
the TESS-only model this yielded 23 free parameters, of which 8 were
physically relevant and 15 were nuisance parameters.  In the combined
TESS and ground-based model, there were an additional 7 transits, and
therefore an additional 21 nuisance parameters for a total of 44 free
parameters.

>>>>

\documentclass[12pt,twocolumn,tighten]{aastex63}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex63}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

\begin{abstract}
  We report the discovery of TOI 837b and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry
  from El Sauce and ASTEP400, and spectroscopy from CHIRON, FEROS, and
  Veloce.  We find that TOI 837 is a $T=9.9$ mag G0/F9 dwarf in the
  southern open cluster IC 2602.  The star and planet are therefore
  $35^{+11}_{-5}$ million years old.  Combining the transit photometry
  with a prior on the stellar parameters derived from the cluster
  color-magnitude diagram, we find that the planet has an orbital
  period of $8.3\,{\rm d}$ and is slightly smaller than Jupiter
  ($R_{\rm p} = 0.77^{+0.09}_{-0.07} \,R_{\rm Jup}$).  From radial
  velocity monitoring, we limit $M_{\rm p}\sin i$ to less than 1.20
  $M_{\rm Jup}$ (3-$\sigma$).  The transits either graze or nearly
  graze the stellar limb.  Grazing transits are a cause for concern,
  as they are often indicative of astrophysical false positive
  scenarios.  Our follow-up data show that such scenarios are
  unlikely.  Our combined multi-color photometry, high-resolution
  imaging, and radial velocities rule out hierarchical eclipsing
  binary scenarios.  Background eclipsing binary scenarios, though
  limited by speckle imaging, remain a 0.2\% possibility.  TOI 837b is
  therefore a validated adolescent exoplanet.  The planetary nature of
  the system can be confirmed or refuted through observations of the
  stellar obliquity and the planetary mass.  Such observations may also
  improve our understanding of how the physical and orbital properties
  of exoplanets change in time.
\end{abstract}

@@

Beyond physical changes, dynamical changes are expected in the
semi-major axes, eccentricities, and stellar obliquities of young
planets.  When the gas disk is present, the planetary semi-major axis
is thought to change in step with the viscous evolution of the disk
\citep{lin_orbital_1996}.  High-eccentricity migration processes
including planet-planet scattering, secular chaos, and Kozai-Lidov
oscillations can also occur \citep[{\it
e.g.},][]{fabrycky_shrinking_2007,chatterjee_dynamical_2008,lithwick_secular_2014}.
The circularization timescale is thought to be such that for any giant
planets that migrated early, their orbits should circularize within
100 million years \citep{zahn_tidal_1977,bonomo_gaps_2017}.

Finding and understanding systems undergoing these evolutionary changes is
a major goal in contemporary exoplanet research.  To identify stars
younger than say 1 \replaced{Gyr}{gigayear}, a number of direct and indirect methods are
available \citep{soderblom_ages_2010}.  The traditional approach is to
isochronally age-date coeval groups of stars, hereafter ``clusters''
\citep[{\it
e.g.},][]{lada_embedded_2003,zuckerman_young_2004,krumholz_star_2019}.
Young field stars can also be identified isochronally, provided that
they are sufficiently massive \citep{berger_gaia-kepler_2020}.  Other
age indicators include stellar rotation periods, the abundance of
photospheric lithium, and chromospheric diagnostics such as calcium
emission and broadband UV emission.  Studies by, for instance,
\citet{david_discovery_2018} and G{.}~Zhou et al{.}~(2020, submitted)
have combined these methods to age-date individual field stars hosting
transiting planets.  Many of these latter methods were summarized by
\citet{mamajek_improved_2008}, and have since been calibrated by, {\it
e.g.},
\citet{irwin_rotational_2009,barnes_color-period_2015,meibom_spin-down_2015,angus_calibrating_2015}
and \citet{curtis_tess_2019} for stellar rotation,
\citet{zerjal_chromospherically_2017} for chromospheric activity, and
{\it e.g.}, \citet{berger_identifying_2018} and
\citet{zerjal_galah_2019} for lithium abundances.

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.77\textwidth]{f1b.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Light curves of \tn.}
    {\it Top}:
    TESS \texttt{PDCSAP} median-subtracted relative flux at 2-minute
    sampling in units of parts-per-thousand ($\times 10^{-3}$).
    Starspot-induced variability is the dominant signal; flares are
    shown with red crosses.  Dashed lines indicate the five transits
    observed by TESS over Sectors 10 and 11.  {\it Middle}: Individual
    TESS transits.  Gray lines are the best-fit model to the TESS
    \added{and ground-based data}, which includes
    a local quadratic trend for each transit. Gray points are 2-minute
    \texttt{PDCSAP} flux measurements, black points are binned to
    15-minute intervals.  {\it Bottom}: Phase-folded TESS and
    ground-based transits. \added{Section~\ref{subsec:groundphot} presents
    the ground-based data.} Gray points are flux
    measurements with the local spot-induced variation removed.  A
    weighted binning at 6-minute intervals yields the black points.
    The black error-bar shows the median uncertainty for the black
    points.  The gray line is the best-fit model for the entire
    dataset.
		\label{fig:thephot}
	}
\end{figure*}

@@

\added{The top panel of} Figure~\ref{fig:thephot} shows the
\added{TESS} data.  The dominant modulation induced by starspots
coming into and out of view has a peak-to-peak amplitude of about
2.3\%, and a period of about 3 days.  The dips are suggestive of a
grazing transiting planet, recurring roughly every 8 days with a depth
of about 0.4\%.  A few flares are also visible.  A phase-folded view
of the TESS transits \deleted{with starspot variability
removed}\added{combined with ground-based follow-up photometry} is
shown in \added{the bottom panel of }Figure~\ref{fig:thephot}.
\added{The ground-based data }and our procedure for fitting the
models \deleted{in these plots is described in }\added{are discussed
in Sections~\ref{subsec:groundphot} and~\ref{subsec:planet}
respectively}.  \added{First though, some prerequisite context on the
stellar neighborhood of \tn\ is needed.}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{ {\bf Scene of \tn.}
    Mean TESS image of \tn\ from Sector~10\added{ on an 11$\times$11
    pixel cutout}, with a logarithmic grayscale\added{ indicating the
    flux in each pixel}. The yellow star is
    the position of \tn.  White circles are resolved Gaia sources with
    $T<16$\replaced{. Brighter stars are larger}{, with brighter stars
    being larger}.  The black \texttt{X} and white \texttt{/} hatches
    show the apertures used to measure the background and target star
    flux, respectively. \replaced{Dashed lines of constant declination
    and right ascension are shown}{The compass shows cardinal
    directions in celestial coordinates. Dashed lines of constant
    declination are separated by 1$'$, while those of right ascension
    are separated by 2$'$}.  Two stars of interest are ``Star A'' and
    ``Star B'', which were excluded as being possible sources of the
    transits.
		\label{fig:scene}
	}
\end{figure}

@@

\added{
An additional line of evidence for Star A not being the transit host
was also noted by the referee.  The $G$-band magnitude and the
parallax suggest that Star A is an M dwarf. As a probable cluster
member, it would have $Bp - Rp \approx 2.8$ (see
Section~\ref{subsec:hr}), which corresponds roughly to a mass in the
range of 0.15-0.45$\,M_\odot$, or densities roughly in the range of
2-3$\,{\rm g}\,{\rm cm}^{-3}$ based on the PARSEC isochrones
\citep{bressan_parsec_2012,chen_improving_2014,chen_parsec_2015,marigo_new_2017}.
These densities are inconsistent with those inferred from the transit
fits in Section~\ref{subsec:planet}.
}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.48\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Velocimetry of \tn.} {\it Top:} Radial velocity (RV)
    measurements, with best-fit instrument offsets and jitter terms
    included.  The expected scatter from starspots based on $v\sin i$
    and the photometric modulation amplitude is
    $\sim$300$\,$m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
    orbital ephemeris of \pn.  The planet is not detected.  The dashed black
    line shows a circular Keplerian orbit representing the 3-$\sigma$
    upper mass limit.
    \label{fig:rvs}
	}
\end{figure}

@@

The spectroscopic line profiles were thoroughly examined for any signs
of secondary lines that might indicate the presence of another star,
either associated or in chance alignment with TOI 837. No such set of
lines was found. To set limits on the contributions of a close-by star
to the observed spectrum, we injected a \replaced{second set of lines
to the mean least-squares deconvolution profile}{secondary signal into
the mean least-squares deconvolution profile} derived from the CHIRON
observations.  The injection spanned 10,000 different combinations of
line broadening, velocity separation, and flux ratio $F_2/F_1$.  The
recovery results showed that for rotational broadenings of the
secondary of $5$, $15$, and $25\,\mathrm{km\,s}^{-1}$, we were able to
exclude sources with flux fractions $F_2/F_1$ brighter than roughly
$0.03$, $0.08$, and $0.20$, provided that the secondary was separated
from the primary by at least $\approx 15\,{\rm km\,s}^{-1}$.  At
smaller velocity separations, the injected lines begin to blend with
the target spectrum.
\added{We verified these results by injecting secondary lines directly
into the spectrum and then deriving its LSD broadening profile as we
would for a normal observation.  The results were nearly identical,
save for greater computational cost.}

@@

Assuming an eclipse has been localized to the target star, potential
false positive scenarios include eclipses of a\added{n unresolved}
background binary (BEB), eclipses of a hierarchical system bound to
the primary star (HEB), and the possibility that the eclipses are
caused by a stellar companion, rather than a planetary one (EB).

@@

In ``Method 2'', we \deleted{simply} used the observed location of
\tn\ in the HR diagram and interpolated against the 40$\,$Myr
\added{MIST} isochrone.  This method leverages the relative location
of \tn\ within the \deleted{narrow} \cn\ isochrone to derive precise,
theoretically self-consistent constraints on all of the stellar
parameters.  Although this approach would fail for a low-mass star,
\tn\ is above the stellar masses where the Gaia photometry and
isochrone models begin to diverge.
\added{
  The statistical uncertainties yielded by this approach are of order
  1\% for the stellar mass and radius.  To quantify the systematic
  uncertainties, we compared the parameters derived from the MIST
  isochrones with those from the
  PARSEC\footnote{\url{http://stev.oapd.inaf.it/cmd}} isochrones
  \citep{bressan_parsec_2012,chen_improving_2014,chen_parsec_2015,marigo_new_2017}.
  The PARSEC isochrones gave a stellar mass 5\% lower, effective
  temperature 3\% lower, logarithmic surface gravity 1\% lower, and
  radius 8\% lower than the MIST isochrones.  For the sake of
  self-consistency, in Table~\ref{tab:starparams} and the ensuing
  analysis we adopted the stellar
  parameter values from MIST.  We took the uncertainties to be the
  quadrature sum of the statistical and systematic components.
}

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f10.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{ 
    {\bf Posterior probabilities of impact parameter, planet-to-star
    size ratio, and stellar density.} Contours are shown at 1, 2, 3,
    and 4-$\sigma$ confidence.  The planet-to-star size ratio
    corresponds to a planet size between \replaced{$0.68\,R_{\rm Jup}$
    and $0.97\,R_{\rm Jup}$}{$0.62\,R_{\rm Jup}$ and $0.95\,R_{\rm
    Jup}$} (3$^{\rm rd}$--97$^{\rm th}$ percentile).  This plot was
    made using \texttt{corner} \citep{corner_2016}.
		\label{fig:subsetcorner}
	}
\end{figure}

We also considered two different approaches for fitting the available
time-series photometry of \pn.  \replaced{To derive the most precise
possible ephemeris,}{In the first approach,} we fitted the ground and
space-based transits simultaneously.  \replaced{To derive the physical
parameters of the planet}{In the second}, we fitted the TESS data
alone\deleted{, due to our better understanding of the underlying
systematic trends and the higher precision}.

To clean the TESS \texttt{PDCSAP} light curve, we first eliminated
points that had quality flags corresponding to any of bits $\{3, 4, 6,
8, 11, 12\}$.  This excluded cadences affected by coarse spacecraft
pointing, reaction wheel desaturation events, manual flags, cosmic ray
hits, and straylight from the Earth or Moon being present.  Inspecting
the data, we also manually excluded the two flares shown in
Figure~\ref{fig:thephot}.  We then trimmed the TESS data to windows of
$\pm 7\,{\rm hr}$ centered on each transit.

Our model for time-series photometry data was an
\citet{exoplanet:agol20} transit with physical and orbital parameters
shared across all transit windows, plus a local quadratic trend
allowed within each window.  Select parameters and priors are listed
in Table~\ref{tab:posterior}, for the \replaced{TESS-only model}{joint
model of the TESS and ground-based data}.  In brief, we fitted for the
shared stellar parameters $\{\log g, R_\star, u_0, u_1\}$, and the
shared planetary parameters $\{t_0, P, b, \log(R_{\rm p}/R_\star)\}$.
There were also three free trend parameters for each transit window to
account for the local rotational variability.  In the TESS-only model
this yielded 23 free parameters, of which 8 were physically relevant
and 15 were nuisance parameters.  In the combined TESS and
ground-based model, there were an additional 7 transits, and therefore
an additional 21 nuisance parameters for a total of 44 free
parameters.
